sdmTMB: Fast, flexible, and user-friendly spatial and spatiotemporal generalized linear mixed-effects models

### 2021-11-27 doc/paper.Rmd
Edit

An sdmTMB model requires a data frame that contains a response column, columns for any predictors, and columns for spatial coordinates.
It usually makes sense to convert the spatial coordinates to UTMs such that distance remains constant throughout the study region (e.g., using `sf::st_transform()`).
Here, we illustrate a spatial model fit to Pacific cod (*Gadus macrocephalus*) trawl survey data from Queen Charlotte Sound, BC, Canada.
Our model contains a main effect of depth as a penalized smoother, a spatial random field, and Tweedie observation error.
Our data frame `pcod` (built into the package) has a column `year` for the year of the survey, `density` for density of Pacific cod in a given survey tow, `depth` for depth in meters of that tow, and spatial coordinates `X` and `Y`, which are UTM coordinates in kilometres.

@@

>>>>

An sdmTMB model requires a data frame that contains a response column, columns for any predictors, and columns for spatial coordinates.
It usually makes sense to convert the spatial coordinates to an equidistant projection such as UTMs such that distance remains constant throughout the study region (e.g., using `sf::st_transform()`).
Here, we illustrate a spatial model fit to Pacific cod (*Gadus macrocephalus*) trawl survey data from Queen Charlotte Sound, BC, Canada.
Our model contains a main effect of depth as a penalized smoother, a spatial random field, and Tweedie observation error.
Our data frame `pcod` (built into the package) has a column `year` for the year of the survey, `density` for density of Pacific cod in a given survey tow, `depth` for depth in meters of that tow, and spatial coordinates `X` and `Y`, which are UTM coordinates in kilometres.

@@

<!-- Future directions para? -->
<!-- multivariate, but only if can keep interface simple -->
<!-- optimized Bayes sampling -->
<!-- residual diagnostics -->
<!-- zero inflation -->
<!-- MVT? time-varying epsilon -->
